Efficient Non-incremental Constructive Solid Geometry Evaluation for Triangular Meshes

### 2016-05-09 summary.tex
change to work office

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference. CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.
\newline

{\color{red}{
Main Contribution:

@@

2. Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex. We develop a propagating to spread the classification information from the seed vertex into the whole CSG. In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.
}}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=7.1in]{flowchart}
\caption{An overview of the proposed method for CSG evaluation. In this toy example, the CSG tree represents a solid constructed by (Cube $\cup$ Sphere - Cylinder). (d) shows how to classify faces step by step using a flood filling algorithm. Faces of the same primitive are grouped as the inter-primitive group. Then faces of the same inter-primitive group are further divided into intra-primitive groups according to their conditions of intersection (c). The unvisited faces are black. Different colors of other faces indicate that they are accepted and belong to different intra-primitive groups. Rejected faces are rendered with wire-frame. The seed face of flood filling in each primitive is highlighted in red.}
\label{fig_overview}
\end{figure*}

CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids. Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces. For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.

Sugihara and Iri \cite{sugihara1990solid} introduced a plane-based representation of polyhedra. They found that Boolean operations are fundamentally robust using the plane equation as the primary geometry representation. In this condition, the evaluation of Boolean operations can be performed with no `constructions' \cite{shewchuk1999lecture}, thereby avoiding the introduction of any numerical errors.

Berstein and Fussell \cite{bernstein2009fast} noted that a binary space partitioning (BSP) merging algorithm in Boolean operations \cite{thibault1987set, naylor1990merging} is actually a plane-based technique. Therefore, they combined the two conceptions---plane-based geometry and BSP merging---to develop an unconditionally robust method for Boolean operations of polyhedra. Using Shewchuk's adaptive geometry predicate technique \cite{shewchuk1997adaptive}, this method can be only twice slower than non-robust methods. Our approach adopts this technique in the stage of face classification to ensure the robustness.

Berstein and Fussell's method does not alleviate the problem of high memory consumption of BSP-based algorithms. Thus, it remains unprepared for polyhedra with massive faces. However, it inspired Campen and Kobbelt to develop a more delicate approach  \cite{campen2010exact}. This approach solves the problem of exact and efficient conversion of polyhedra between vertex-based and plane-based representations. Moreover, by leveraging the adaptive octree, BSP structures are nested into octree cells where the intersection between primitives occurs. For efficiency, face classification is performed using cells as the basic classification units. This localized scheme saves considerable computing resources and retains the topology of non-intersected areas.

Such localized scheme is widely used in different methods of CSG boundary evaluation \cite{pavic2010hybrid, wang2011approximate, feito2013fast, campen2010exact}. These methods are usually based on intersection computation and face membership classification. The success of such localized scheme is enabled by two facts. First, the intersections between primitives are locally distributed. Second, space labels of a face are often coherent with those of its neighborhood. The former makes it possible to reduce the space that requires an intersection test. The latter enables sharing of space labels between adjacent faces to accelerate face classification.

However, most of these methods use the cube (e.g., voxels, octree cells) as the unit of the face group, which is often the natural result of reusing space-division data structures constructed for intersection computation. In this way, connected faces that share the same labels might be distributed in different cubes. Thus, repetitive classifications may be required for each cube. Furthermore, faces of different classifications may coexist within a small space, forming a ‘mixed’ area (e.g., the red areas in Figs. \ref{fig:cluster}(a) and (b)). Because the size of the cubes cannot be illimitably small, special cubes that contain faces with different space labels typically must be constructed in these mixed areas. Processing these special cubes is often complex and time-consuming. To more efficiently share space labels, we therefore use faces, rather than cubes, as the basic grouping units. Grouping is efficiently performed by utilizing geometry connectivity with a flood-filling algorithm.

Recently, Feito et al. \cite{feito2013fast} proposed a method for Boolean evaluation. This method also uses a face-based grouping scheme. To share classification results, faces that do not intersect with other primitives are grouped together according to geometry connectivity. This method and the proposed method have similar stages for single Boolean operation evaluation. One of the major differences is that our method supports non-incremental evaluation of CSG. For this purpose, we designed a series of dedicated stages. Additionally, our face grouping scheme is intended for both non-intersected faces and faces that intersect with other primitives. It thus provides a uniform treatment for all faces and further accelerates the face classification stage. Moreover, the similarity between adjacent groups is omitted by Feito et al.'s method. Although different groups have different space labels, we observe that they may still share some of these labels if they are neighboring. We utilize this kind of space label coherence between groups for better performance.

On the other hand, with the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations. These methods often have good performance and are suitable for interactive applications, such as digital sculpting. However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.

\section{Overview}

\label{sec:overview}

As in most previous works \cite{feito2013fast, bernstein2009fast}, we require the input primitives of the CSG tree to be watertight Nef polyhedra with manifold surfaces. We assume there is no self-intersection. Because we adopt a flood-filling strategy, we additionally assume that the connectivity of adjacent faces is available. Our current implementation is dedicated to primitives of triangular meshes for simplicity. Our approach efficiently and robustly computes the boundary of CSG solids in three steps, as illustrated in Fig. \ref{fig_overview}. Our main contributions exist in Steps 2 and 3.

\subsection{Adaptive Octree Construction}

As a typical routine of localization, our method uses the adaptive octree to frequently accelerate the used spatial query afterwards. Our octree construction implementation is akin to the implementation in Feito et al.'s method \cite{feito2013fast}. The major difference is that, because our method is for non-incremental CSG evaluation, the octree is constructed on the bounding box that contains all input primitives (Fig. \ref{fig_overview}(b)). To avoid presentation ambiguity between a CSG leaf and an octree leaf, the latter is called a cell. Intersection detection between triangle faces and cells can be efficiently performed by using the separating axis theorem \cite{gottschalk1996obbtree}. Cells are classified into two types: if all triangles that intersect a cell belong to the same primitive, we call it a \emph{non-critical} cell. Otherwise, it is a \emph{critical} cell. This classification is needed for intersection computation in the next step.

\subsection{United Representation of Intersection Construction}
\label{sec:overview:isect}

\subsection{Multilevel Flood-filling Classification}

\section{United Representation of Primitive Intersection}
{\color{red}{
Primitive intersects primitive, generating intersection line segments (Fig. \ref{fig_raw1}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw1}\\
  \caption{triangle contains intersection lines, two-primitive case}\label{fig_raw1}
\end{figure}

Considering degenerate cases in n-primitives CSG can be very complex (Fig. \ref{fig_raw2}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw2}\\
  \caption{triangle contains intersection lines, n-primitives degenerate cases}\label{fig_raw2}
\end{figure}

We converted it into a united representation, making it clear and easy to process by the following process (Fig. \ref{fig_raw3}).

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{raw3}\\
  \caption{triangle contains intersection lines, n-primitives degenerate cases, using united representation}\label{fig_raw3}
\end{figure}
}}

\subsection{Plane-based Triangle Intersection}

{\color{red}{why using triangle intersection, rather than edge-face based, etc. --- for coplanar test.}}
\newline\newline

@@

M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig. \ref{fig_projection}. First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$. This is a necessary condition of intersection between $F_1$ and $F_2$. If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$. Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed . At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .

@@

We first convert $F_1$ and $F_2$ into their respective plane-based representations: a supporting plane surrounded by three bounding planes (Fig. \ref{fig:p-reps}). We implement this conversion using the exact conversion method by Campen and Kobbelt \cite{campen2010exact}. Then, in our implementation, the relative position of a point and a plane can be determined by computing the sign of the multiplication of determinants \cite{sugihara1990solid}. To avoid introducing errors, we represent the end points of $Seg_1$ and $Seg_2$  by intersections of plane triples, rather than by directly computing their coordinates. As illustrated in Fig. \ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face. Because the edge line of $F_1$ can be represented as $[S_1, S_X]$ (or $[S_2, S_X]$ for an edge line of $F_2$), where $S_X$ is the corresponding bounding plane of the edge, the end points of $Seg_1$ or $Seg_2$ can be represented in the form of $[S_1,S_2,S_X]$. In Fig. \ref{fig:isect}, we list all intersection situations between a triangle and a plane, and the $S_X$  in each situation.

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{sign}
\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$. All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$. End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
\label{fig:isect}
\end{figure}

The intersection between $F_1$ and $F_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig. \ref{fig_projection}), where $L$ is the intersection between $S_1$ and $S_2$. Unlike M\"{o}ller's implementation, our approach uses no projection, which requires the exact point coordinates. We call the direction of vector $\vec{N}_1\times \vec{N}_2$ the positive direction, where $\vec{N}_1$ and $\vec{N}_2$ are normals of $S_1$ and $S_2$ respectively. Given two points $A$ and $B$ on $L$,  we compute the sign of the multiplication of determinants:
\begin{equation}
\label{eq:sign}
  K(A, B)=
  \left|
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{S}_1 \\ \vec{S}_2 \\ \vec{S}_A \\ \vec{S}_B
  \end{array}
  \right|
  \left|                 %左括号
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_A
  \end{array}
  \right|
  \left|                 %左括号
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_B
  \end{array}
  \right|,
\end{equation}
where $\vec{S}_X$ is the coefficient vector of plane equation $[a_X,b_X,c_X,d_X]$,  and $ \vec{N}_X$ is the normal vector $[a_X,b_X,c_X]$. If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$. Otherwise, $A$ and $B$ are concident.

If $F_1$ and $F_2$ are coplanar, we check whether they overlap within the common plane using the algorithm by M\"{o}ller\cite{moller1997fast}. The substrate of this algorithm is to verify on which side of an edge $E$ a point $V$ lies. We implement it using plane-based geometry by substituting $E$ with its corresponding bounding plane $S_E$ and then computing the sign of distance from $V$ to $S_E$.

\subsection{Generating United Representation}

{\color{red}{Mainly deal with intersection between intersection line segments.}}

@@

{\color{red}{Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.}}

In this step, we classify faces one by one to generate the final mesh. The intersection information computed in the previous section is used for re-tessellation and space label computation. To better explain our approach, we firstly introduce the background knowledge. Then the framework of this step is outlined. Afterwards, several important techniques in this step are detailed.

@@

We firstly introduce the space labels, which comprise the basis of face membership classification. The space label of face $F$ with respect to primitive $M$, denoted as $L_F(M)$, is the relative location of $F$ with respect to $M$. Also, we use $L(M)$ to denote the space label with respect to $M$ which does not specify a face. In general, space label has four conditions: completely inside (\emph{In}), completely outside (\emph{Out}), on the boundary (\emph{On}) or not available (\emph{N/A}). In the last condition, $F$  crosses the boundary of $M$. Accordingly, it does not have a uniform label. In addition, if the normal direction of $F$ is considered, there are two derived conditions of \emph{On}: the normal points to the outside (\emph{Same}) and those to the inside (\emph{Oppo}) of $M$.

The evaluation of Boolean operations between B-reps primitives $A$ and $B$ can be converted to the problem of surface selection according to the labels \cite{kuratowski1968set}:
\begin{equation}
\label{eq:select}
\begin{split}
&A\cup^*B:\{F_A~Out~B\}\cup\{F_B~Out~A\}\cup\{F_A~Same~B\},\\
&A\cap^*B:\{F_A~In~B\}\cup\{F_B~In~A\}\cup\{F_A~Same~B\},\\
&A-^*B:\{F_A~Out~B\}\cup\{(F_B~In~A)'\}\cup\{F_A~Oppo~B\},
\end{split}
\end{equation}

\noindent where $F_X$ is the faces of $X$, and $F'$ means $F$ with an inverted normal. The stars ($^*$) after the operation notations ($\cup, \cap, -$) mean that the Boolean operations are regularized.

Now, consider computing $L_F(T)$, where $T$ is a CSG solid $T$ with $n$ primitives $\{M_i~| ~i = 1,2,3,...,n\}$.  Then there are a total of $n$ space labels for $F$: \{$L_F(M_i)~|~i = 1,2,3,...,n\}$ (or in vector form $\vec{L}_F$). If all elements in $\vec{L}_F$ are known and none of them is \emph{N/A}, $L_F(T)$ can be easily computed by traversing the whole CSG tree from bottom to top and progressively combining the space labels of the CSG nodes according to combination rules \cite{requicha1985boolean}:
\begin{equation}
\label{eq:comb}
\begin{split}
X\cup Out\Rightarrow X, ~~&X\cap Out\Rightarrow Out, \\
X\cap In~~\Rightarrow X, ~~&X\cup In\Rightarrow In, \\
X \cup X \Rightarrow X, ~~&X \cap X \Rightarrow X,\\
Same \cup Oppo\Rightarrow In, ~~&Same \cap Oppo\Rightarrow Out,
\end{split}
\end{equation}
where $X$ is an arbitrary label value. Note that the combination rules for difference operation are not shown here, because the difference operation can be converted into the intersection operation using De Morgan's transformations:
\begin{equation}
\label{eq:demo}
\begin{split}
A-B\Rightarrow A\cap B^c, ~~~~~~~&(A^c)^c\Rightarrow A,\\
(A\cap B)^c\Rightarrow A^c\cup B^c, ~~&(A\cup B)^c\Rightarrow A^c\cap B^c,
\end{split}
\end{equation}
where $X^c$ denotes the complement of $X$. If and only if $L_F(T) = Same$, $F$ lies on the boundary of the final model and has the correct normal; accordingly, $F$ belongs to the final result.

If some elements in $\vec{L}_F$ are \emph{N/A} or cannot be computed, we may be unable to compute $L_F(T)$. However, the CSG tree $T$ can be trimmed into a smaller one with fewer primitives to reduce the complexity of further evaluation. For example, assume we have a CSG with its Boolean expression $M_1\cup (M_2\cap M_3-M_4)$. Given the values of two labels $L(M_1)=Out$, $L(M_2)=In$, the expression can be rewritten as $Out\cup (In\cap M_3-M_4)$. Using the combination rules we can simplify the expression as $M_3-M_4$. Thus, any face that shares the same two labels $L(M_1)$ and $L(M_2)$ can be classified based on the trimmed CSG tree $M_3-M_4$, which has only two primitives.

\subsection{Face Classification Framework}
\label{sec:framework}

\begin{figure}
\centering
\includegraphics[width=3.5in]{multilvl}
\caption{Illustration of multi-level face grouping framework. Faces are grouped into smaller groups in each level. The trimmed CSG tree of a specific group is obtained by trimming the tree of its parent according to common labels of this group. When the group is not further subdivided, faces in this group are respectively classified based on the trimmed CSG tree of this group.}
\label{fig:hierachy}
\end{figure}

Space labels of neighboring faces are often coherent. That is, given two neighboring faces $F_1$ and $F_2$, $L_{F_1}(M)$ and $L_{F_2}(M)$ are often the same. Therefore, we can group together neighboring faces and evaluate them based on the smaller CSG tree, which is trimmed by the common labels. The trimmed tree contains fewer leaves, thus enabling faster computation. If face grouping can be efficiently performed, this strategy will greatly accelerate the process of face membership classification. Moreover, a multi-level grouping scheme (Fig. \ref{fig:hierachy}) may provide even greater capability to shared labels. By using such a scheme, faces are first grouped into first-level groups; then, faces of the same first-level groups are further divided into second-level groups, and so on. Labels are shared in each level and the original CSG tree is trimmed step by step according to common labels in each level. We developed this idea into a novel classification algorithm that uses a two-level grouping scheme. The first level is the \emph{inter-primitive} level; the second is the \emph{intra-primitive} level.

Before we begin face classification, pre-computation is conducted to make the subsequent analysis easier. The original CSG tree is converted into a \emph{positive} tree using the method by Rossignac and Voelcker \cite{rossignac1988active}. `Positive' means that the CSG tree contains no difference (-) operation. According to Equation \ref{eq:demo}, there may be some primitives with complement notation. The benefit is that we are not required to consider the difference operations in the following computation.

The classification starts from face grouping in the inter-primitive level. In this level, faces of the same primitives are simply grouped together. Then, we give a rough estimation of the common labels of the group. Suppose the group is primitive $M$. Its face labels with respect to primitives whose bounding boxes are totally outside of $M$'s bounding box must be $Out$ (for primitives with complement notations, $In$). The original CSG tree is trimmed into the first trimmed CSG tree (as short as the \emph{the first trimmed tree}) according to these common labels plus an extra label $L(M)$ whose value is obviously $Same$.

After that, the inter-primitive groups are further divided into smaller intra-primitive groups. To explain how to perform intra-primitive grouping, we firstly introduce an essential concept---intersection primitive (IP). The IPs of a face $F$ is defined as the primitives that $F$ intersects, excluding the primitive to which $F$ belongs (denoted as $M$). Primitives (excluding $M$) that do not intersect $F$ are called non-IPs. The set that contains all IPs of $F$ is the IP-set of $F$. That set can be computed by enumerating all the primitives in the cross list and coplanar list of $F$.

Now, we require that the faces of the same intra-primitive group meet two requirements: they should be connected together and have the same IP-set. These two requirements give these faces very good properties, as discussed in Proposition 1. The labels referenced in Proposition 1 are used to trim the first trimmed tree into the second trimmed CSG tree (as short as \emph{the second trimmed tree}). For a specific intra-primitive group, the primitives of its second trimmed tree is a subset of the common IP-set of that group. This is because all space labels with respect to non-IPs are shared within the intra-primitive group and all these labels are either $In$ or $Out$. Therefore, all non-IPs must have been trimmed from the CSG tree (to be explained in Section \ref{sec:trim}).

\vspace{0.8em}
\noindent \textbf{Proposition 1.}~~~~If a group of faces are connected together and they have the same IP-set, they must share the same labels with respect to all non-IPs. These labels are either \emph{In} or \emph{Out}.

\vspace{0.6em}
\noindent \textbf{Proof.}~~~~We only prove that the conclusion stands for adjacent faces, which is a special case of connected faces. Promoting the conclusion to the general situation is obvious. Assume $M$ is a non-IP and label $L(M)$ is different for the two adjacent faces $A$ and $B$ . Then there must be faces from $M$ between $A$ and $B$ to cause the different space labels. Additionally,  because $A$ and $B$ are adjacent, at least one of $A$ and $B$ intersects the faces from primitive $M$. This contradicts the assumption that $M$ is non-IP. Therefore, $L(M)$ must be the same for $A$ and $B$. Moreover, because $M$  is non-IP, $L(M)$ is either \emph{In} or \emph{Out}.

\begin{figure}
  \centering
  \includegraphics[width=3.5in]{mesh}\\
  \caption{A snapshot during flood filling (\emph{left}), and the final grouping result (\emph{right}). Different intra-primitive groups are distinguished by different colors. From the final grouping result, the whole mesh is divided into 9 intra-primitive groups.}\label{fig:mesh}
\end{figure}

>>>>

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

Main Contribution:

@@

2. Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex. We develop a propagating to spread the classification information from the seed vertex into the whole CSG. In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.

@@

\section{Background}

\subsection{Plane-based geometry}

\subsection{CSG evaluation}

\section{Overview}
费大幅度发
\label{sec:overview}

\iffalse
\begin{figure*}[!t]
\centering
\includegraphics[width=7.1in]{flowchart}
\caption{}
\label{fig_overview}
\end{figure*}
\fi

Our method follows the paradigm of two-step Boolean operation---intersection detection and facet classification, together with an extra step of pre-computation to accelerate the intersection detection. The main feature of our method is that we design a unified representation of intersection between primitives (U-rep) to control the complexity of intersection detection result and simplify the facet classification. Also, plane-based representation is applied throughout the methods to ensure no error introduced. For the same reason, we compute indicator vectors of vertices rather than of the barycenter of facets during classification and deduce the facets' indicator vectors from its vertices'.

\subsection{Space division}

This step is the mainly the preparation for intersection detection. As intersection detection is performed between each pair of faces, localization is necessary for acceleration by filtering invalid pairs. In general, any space division data structure can be applied in this stage. For simplicity, our method uses the adaptive octree. The implementation is akin to the implementation in ?? et al.'s method \cite{feito2015fast}. Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{non-critical cell}. Otherwise, it is a \emph{critical cell}. The big difference between our construction method and ??'s is the subdivision termination condition. In ??'s method,??. However, in our method, we do not need subdivide any non-critical cell no matter how many faces it contains. This is because subdividing non-critical cells benefits only the polyhedron inclusion test, which is frequently used in ??'s method but rarely in ours. This simplification can bring large performance advantage, especially for those cases whose intersection areas are small.

\subsection{Intersection detection}

The goal of this step isIntersection detection is performed between pairs of triangle faces within each critical cell. For the sake of robustness, all degenerated cases should be classified and well-handled.

\subsection{United representation of intersection}
\label{sec:overview:isect}

\subsection{Flood-Filling facet classification}

\section{Construction of United Intersection Graph }

The intersection of primitives can be very complex because of so many degenerate cases. In order to design a robust algorithm, one have to take into consideration of all the degenerated cases, which often makes the algorithm rather complex and error-prone to implement. We observe the important fact that the CSG evaluation is no more than splitting and selecting faces. Therefore, the only important thing during intersection test is to find out the potential edges and vertices of the result mesh. Therefore, we use a very concise graph model, with only a few extra data for classification on vertices, as the output of this stage.

Another problem is that numerical error introduced by computing coordinates of intersection vertices often leads to fault topology construction in the later stage. Using high precision float point is the most common way to alleviate this issue. However, only the time-consuming rational number arithmetic can be absolutely precise.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.5in]{p-reps}\\
  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies. }\label{fig_p-reps}
\end{figure}

 In order to be both robust and efficient, we choose not to compute the coordinates of intersection vertices until we finally construct the result topology. In the early stage, each new vertex is represented by intersection of three planes. This method is based on two facts: 1) Douze et al. [] observe that every intersected vertex is either the intersection between an edge and a plane, or the intersection of three planes. 2) Campen et al. [] give an efficient method to precisely convert b-reps mesh into its plane-based representation (Fig. \ref{fig_p-reps}). Details is explained in the following.

\subsection{Definition}

Faces in a certain primitive can be classified into intersected faces and non-intersected ones according to whether they intersect other primitives. Our United Intersection Graph (UI-graph) is a graph data structure embedded in each intersected face. It is used to split these faces and guide the face classification.

The nodes of UI-graph of an intersected face $F$ are the vertices, include the original three corners of $F$ and all the intersected vertices within $F$. Intersected vertices are shared between different UI-graphs. For example, the vertex $a$ is generated by intersection between face $F_1$ from primitive $P_i$ and edge $e(G_1, G_2)$ from primitive $P_j$, where $e(G_1, G_2)$  is the shared edge of face $G_1$ and face $G_2$. Then face $F_1$, $G_1$, $G_2$ are all intersected faces and each of them contains a UI-graph with one of its node is $a$.

Douze et al. [] observed that vertices during a CSG evaluation can be divided into three types. The first order vertex is already contained in the input primitives. The second order vertex is the intersection between an edge and a face. The third vertex results from intersection of three faces from different primitives. Considering the degenerate cases, this classification is not complete because different types do overlap. But it does not matter because each vertex at least belong to one of these types. Then we can use the plane-based representation (Fig. \ref{fig_p-reps}) introduced by Campen et al.[], which treats each triangle face by a supporting plane surrounded by three bounding planes, to represent each vertex by intersection of three planes. This method has two advantages. First, it is universal for all kinds of vertices, thus is easy to handle. Second, we can avoid explicitly computing the coordinates of new introduced vertices to avoid introducing numerical error.

Also, each node contains data structure called vertex context. It records on which primitives and on which part of primitive the node lies. A vertex can lies on the vertex, edge or within the face of a certain primitive. For example, the vertex context of $a$ is $\{(F_1, P_i), (e(G_1, G_2), P_j)\}$. This information is very important for the classification of the neighborhood. In particular, we notice that the vertex context of a certain vertex is invariant in different UI-graphs. So we only need to maintain one context for each vertex and shared among UI-graphs.

The edges of UI-graph are simply the intersection line segments between faces of different primitives. They are represented by two references of the nodes in the UI-graph. No further information is required.

As will explained below, we take two steps to construct UI-graphs for each intersected faces of the whole CSG. The first step is to build stand-alone UI-graphs for each pair of primitives, which is built upon our plane-based triangle-triangle intersection test, and the second step is to merge them into a single one for each intersected faces.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.7in]{raw3}\\
  \caption{The UI-graph of a certain face. }\label{fig_raw3}
\end{figure}

\subsection{Plane-Based Triangle-Triangle Intersection}

@@

The plane-based triangle-triangle intersection (PTTI) test is largely the variant of M\"{o}ller's triangle intersection test []. M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig. \ref{fig_projection}. First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$. This is a necessary condition of intersection between $F_1$ and $F_2$. If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$. Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed . At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .

@@

We first convert $F_1$ and $F_2$ into their respective plane-based representations: a supporting plane surrounded by three bounding planes (Fig. \ref{fig:p-reps}). We implement this conversion using the exact conversion method by Campen and Kobbelt \cite{campen2010exact}. Then, in our implementation, the relative position of a point and a plane can be determined by computing the sign of the multiplication of determinants \cite{sugihara1990solid}. To avoid introducing errors, we represent the end points of $Seg_1$ and $Seg_2$  by intersections of plane triples, rather than by directly computing their coordinates. As illustrated in Fig. \ref{fig:isect}(a), these points are the intersection between an edge line of a face and the supporting plane of the other face. Because the edge line of $F_1$ can be represented as $[S_1, S_X]$ (or $[S_2, S_X]$ for an edge line of $F_2$), where $S_X$ is the corresponding bounding plane of the edge, the end points of $Seg_1$ or $Seg_2$ can be represented in the form of $[S_1,S_2,S_X]$. In Fig. \ref{fig:isect}, we list all non-coplanar intersection situations between a triangle and a plane, and the $S_X$  in each situation.

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{sign}
\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$. All the four non-coplanar conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$. End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
\label{fig:isect}
\end{figure}

The intersection between $F_1$ and $F_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by comparing the end points of $Seg_1$ and $Seg_2$ along $L$ (Fig. \ref{fig_projection}), where $L$ is the intersection between $S_1$ and $S_2$. Unlike M\"{o}ller's implementation, our approach uses no projection, which requires the exact point coordinates. We call the direction of vector $\vec{N}_1\times \vec{N}_2$ the positive direction, where $\vec{N}_1$ and $\vec{N}_2$ are normals of $S_1$ and $S_2$ respectively. Given two points $A$ and $B$ on $L$,  we compute the sign of the multiplication of determinants:
\begin{equation}
\label{eq:sign}
  K(A, B)=
  \left|
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{S}_1 \\ \vec{S}_2 \\ \vec{S}_A \\ \vec{S}_B
  \end{array}
  \right|
  \left|                 %左括号
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_A
  \end{array}
  \right|
  \left|                 %左括号
  \begin{array}{c}   %该矩阵一共3列，每一列都居中放置
  \vec{N}_1 \\\vec{N}_2 \\\vec{N}_B
  \end{array}
  \right|,
\end{equation}
where $\vec{S}_X$ is the coefficient vector of plane equation $[a_X,b_X,c_X,d_X]$,  and $ \vec{N}_X$ is the normal vector $[a_X,b_X,c_X]$. If $K(A, B)$ is positive (negative), this means that $A$ lies in the positive (negative) direction of $B$. Otherwise, $A$ and $B$ are coincident.

One may find that we do not give the solution of coplanar cases. This is deliberate because we find recording coplanar cases is not necessary for the following process. This will be discussed further in Section 5.

\subsection{Generating Pairwise UI-Graphs}

As a general case, an intersected face intersects with one or more primitives. This means there could be so many different types of degenerate cases, that it is not easy

we choose divide and conquer \cite{ogayar2005point} \cite{douze2015quickcsg}

We first consider constructing UI-graph between each pair of primitives. The graph generated by two primitives is much simpler than a n-primitive one: since input primitives are not self-intersected, there is no cross or overlap between intersection line segments.

When PTTI test detects a intersection, it outputs the two end points of intersection line segment, or, in a degenerate case, two coincident points.

\subsection{Merging UI-Graphs}

Mainly deal with intersection between intersection line segments. It is necessary when a face intersects with faces from more than one other primitives.

Atom operation:

1. add an vertex. no need outside a graph

2. remove/add edges.

3. sort along an edge.

4. merge vertices.

comparison:

 If coplanar (collinear), choose a direction as positive. 3-4-2
 If not, compute intersection, 4-2

@@

Flood-filling is all about giving a seed and propagation. In this chapter, from down to top, we introduce this process and explain how it can save computation time.

@@

\subsection{Flood-filling Inside a Triangle}

\subsubsection{Compute indicator vector}

How to propagate the indicator vector from the seed vertex to all the vertex in a triangle.

Start from a full indicator

\subsubsection{Facet classification}

How to generate new face and classify faces using indicator vector.

\subsubsection{Acceleration}

How to reuse the indicator vector of neighbouring vertex.

\subsubsection{Coplanar degenerate case}

Special case discussion, mainly for coplanar problem.

\subsection{Flood-filling Through CSG Primitives}

\subsubsection{Seed generation}

\subsubsection{Flood-filling within primitives}

\subsubsection{Flood-filling between primitives}

\subsubsection{Acceleration}
